Philosophy of Distributional Semantics\\ \large Best Practices for the Application of Computational Methods to Questions of Meaning

### 2017-05-28 pds/Paper/pds_references.tex
good portion of 2 added

%DS Papers

>>>>

@misc{principles,
  title = {{Discrimination algorithms disparate impact} Kernel Description},
  howpublished = {\url{https://www.theatlantic.com/business/archive/2015/09/discrimination-algorithms-disparate-impact/403969/
}},
  note = {Accessed: 2017-05-22}
}
@article{sweeney2013discrimination,
  title={Discrimination in online ad delivery},
  author={Sweeney, Latanya},
  journal={Queue},
  volume={11},
  number={3},
  pages={10},
  year={2013},
  publisher={ACM}
}

@PROCEEDINGS{proceedings,
  title = {Proc.\ o.t. First Workshop on Ethics in NLP
      (Valencia, Spain, April 2017)},
  booktitle = {Proc.\ o.t. First Workshop on Ethics in NLP
      (Valencia, Spain, April 2017)},
  volume = 1,
  series = {},
  publisher = {},
  address = {Valencia, Spain},
  year = {2017}
}

@inproceedings{leidner2017ethical,
  author =       {Jochen L. Leidner, Vassilis Plachouras},
  title =        {Ethical by Design: Ethics Best Practices for Natural Language Processing},
  crossref =     {proceedings},
  pages =        {9--18},
}

%DS Papers
@article{wagner2015s,
  title={It's a man's wikipedia? Assessing gender inequality in an online encyclopedia},
  author={Wagner, Claudia and Garcia, David and Jadidi, Mohsen and Strohmaier, Markus},
  journal={arXiv preprint arXiv:1501.06307},
  year={2015}
}
@article{harris1954distributional,
  title={Distributional structure},
  author={Harris, Zellig S},
  journal={Word},
  volume={10},
  number={2-3},
  pages={146--162},
  year={1954},
  publisher={Taylor \& Francis}
}
@article{boleda2016formal,
  title={Formal Distributional Semantics: Introduction to the Special Issue},
  author={Boleda, Gemma and Herbelot, Aur{\'e}lie},
  journal={Computational Linguistics},
  year={2016},
  publisher={MIT Press}
}
@article{chowdhury2003natural,
  title={Natural language processing},
  author={Chowdhury, Gobinda G},
  journal={Annual review of information science and technology},
  volume={37},
  number={1},
  pages={51--89},
  year={2003},
  publisher={Wiley Online Library}
}
@inproceedings{bolukbasi2016man,
  title={Man is to computer programmer as woman is to homemaker? debiasing word embeddings},
  author={Bolukbasi, Tolga and Chang, Kai-Wei and Zou, James Y and Saligrama, Venkatesh and Kalai, Adam T},
  booktitle={Advances in Neural Information Processing Systems},
  pages={4349--4357},
  year={2016}
}
